Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-13 paper/sheaf_lics.tex
abstract updated

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

@@

@@

  Sheafification is a popular tool in (higher) topos theory which
  allows to extend the internal logic of a topos with new
  principles. One of the most famous applications is the possibility to
  transform a topos into a boolean topos using the dense topology, which
  corresponds in essence to Gödel's double negation translation. 
  % 
  The same construction has not been considered in Martin-Löf type
  theory because of a mismatch between topos and type theory. This
  mismatched has been fixed recently by considering homotopy type
  theory, an extension of Martin-Löf type theory with new
  principles inspired by category theory and homotopy theory.
  % 
  In this paper, we give a computer checked construction of
  Lawvere-Tierney sheafification in homotopy type theory, which allows
  in particular to give a meaning to the (propositional) law of
  excluded middle inside homotopy type theory, without axiom.

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{xspace}

@@

\newcommand{\ie}{i.e,\xspace}
\newcommand{\eg}{e.g,\xspace}

@@

  Sheafification is a popular tool in (higher) topos theory which
  allows to extend the internal logic of a topos with new
  principles. One of its most famous applications is the possibility
  to transform a topos into a boolean (classical) topos using the
  dense topology, which corresponds in essence to Gödel's double
  negation translation.
  % 
  The same construction has not been considered in Martin-Löf type
  theory because of a mismatch between topos theory and type theory. This
  mismatched has been fixed recently by considering homotopy type
  theory, an extension of Martin-Löf type theory with new
  principles inspired by category theory and homotopy theory, and
  which corresponds closely to higher toposes.
  % 
  In this paper, we give a computer-checked construction of
  Lawvere-Tierney sheafification in homotopy type theory, which allows
  in particular to give a meaning to the (propositional) law of
  excluded middle inside homotopy type theory, without axiom, being
  compatible with the full type-theoretic axiom of choice.
